The Ghost in the Machine: Emergence of Computation through dynamics in CW-complexes

### 2024-06-22 neural-computer-neurips/paper_neurips.tex
playing with formats

Additionally, we are exploiting this relationship by carefully crafting a modified transformers model so we can benefit from several engineering tools, techniques, softwares and hardware that have been matured and extensively tested given the popularity and widespread use of transformers. Further studies are required to develop and validate a better architecture that better represents Neural Population Dynamics.

@@

\subsection{Retrieval of style files}

The style files for NeurIPS and other conference information are available on the World Wide Web at  \url{http://www.neurips.cc/}. The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the various formatting requirements your NeurIPS paper must satisfy.

The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+, rewritten for \LaTeXe{}. \textbf{Previous style files for \LaTeX{} 2.09,  Microsoft Word, and RTF are no longer supported!}

@@

>>>>

Additionally, we are exploiting this relationship by carefully crafting a modified transformers model so we can benefit from several technological advancements in how models are trained at scale ( \cite{DBLP:journals/corr/abs-1910-02054}, \cite{DBLP:journals/corr/abs-2201-11990}, \cite{DBLP:journals/corr/abs-2104-04473}, \cite{DBLP:journals/corr/abs-2001-08361} ), these advancements have been matured and extensively tested at production given the popularity and widespread use of transformers. Further studies are required to develop and validate a better architecture that better represents Neural Population Dynamics.

% ZeRO: Memory Optimizations Towards Training Trillion Parameter Models \cite{DBLP:journals/corr/abs-1910-02054}

% Using DeepSpeed and Megatron to Train Megatron-Turing NLG 530B \cite{DBLP:journals/corr/abs-2201-11990}

% Efficient Large-Scale Language Model Training on GPU Clusters \cite{DBLP:journals/corr/abs-2104-04473}

% Scaling Laws for Neural Language Models \cite{DBLP:journals/corr/abs-2001-08361}

@@

% \subsection{Retrieval of style files}

% The style files for NeurIPS and other conference information are available on the World Wide Web at  \url{http://www.neurips.cc/}. The file \verb+neurips_2019.pdf+ contains these instructions and illustrates the various formatting requirements your NeurIPS paper must satisfy.

% The only supported style file for NeurIPS 2019 is \verb+neurips_2019.sty+, rewritten for \LaTeXe{}. \textbf{Previous style files for \LaTeX{} 2.09,  Microsoft Word, and RTF are no longer supported!}

@@

At the book Shagrir - The Nature of Physical Computation \cite{shagrir2022nature}

A physical system P is a computing system just in case:

\begin{enumerate}
    % ---------------------------------------------------------------------------------
    % 1-Input-Output Mirroring
    % ---------------------------------------------------------------------------------
    \item \textbf{Input-Output Mirroring}. The input-output function, g, of a given process in \textbf{P} preserves a certain relation, \underline{R}, in a target domain \textbf{T}: there is a mapping from \textbf{P} to \textbf{T} that maps g to \underline{R}, x to \underline{x}, y to \underline{y}, \dots , such that $g(x) = y$ iff $\left\langle \underline{x},\underline{y} \right\rangle\ \; \epsilon \; \underline{R}$. This means that g and \underline{R} share some formal relation \textbf{f}.
    % ---------------------------------------------------------------------------------
    % 2-Implementing
    % ---------------------------------------------------------------------------------
    \item \textbf{Implementing}. This process of \textbf{P}, whose input-output function is g, implements some formalism \textbf{S} whose input-output (abstract) function is \textbf{f}.
    % ---------------------------------------------------------------------------------
    % 3-Representing
    % ---------------------------------------------------------------------------------
    \item \textbf{Representing}. The input variables x of \textbf{P} represent the entities \underline{x} of \textbf{T}, and the output variables y of \textbf{P} represent the entities \underline{y} of \textbf{T}.
    % ----------------------------------------------------------------
\end{enumerate}

The underlined italicized symbols (such as x and y) to signify properties of the target domain.
